### 2019-02-27 papers/journal/model.tex

\textbf{Fusion condition in BMC and SMT:}
$\pairs$ defines which molecules can fuse with which molecules.
%
Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
%
$\nodef$ and $\edgef$ are used to define activity of molecules on
nodes and edges respectively.
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We call $G$ {\em well-structured} if molecules $M$ is divided into
two equal-sized partitions $M_1$ and $M_2$ such that
$P \subseteq M_1 \times M_2$, and
for each $(n,M',n') \in \edges$, $n \neq n'$, 
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In other words, a well-structured VTS has no self loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.

We will also consider several variations of the model.
%
For example, unique edge between two nodes, activity of molecules is
not constrained by $\nodef$ and $\edgef$, etc.
%

\textbf{Fusion condition in QBF and synthesis:}
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
two partitions $Q$ and $R$ such that
for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
%
In other words,
molecules are of two types $Q$ and $R$,
%
pairing relations have sets of four molecules such that three
are of one type (??) and one is of another type (??).
%
% This distinction of molecules is due to section~\ref{mol-types}.
%
We call $G$ {\em well-structured} if it is pair compatible, and
for each $(n,M',n') \in \edges$, $n \neq n'$ and
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In addition to fuse compatibility, the well-structured property requires that
here are no self loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.
%
An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with its destination node $n'$
and can not fuse with any other node.
%
$\pairs$ models biological possible quadruple of molecules that participate in fusion.
%
Each edge must be uniquely supported by such a quadruple of molecules.
%
We also require three of them to be on the node or edge, and the forth one
to be on the other side of the fusion.
% $\pairs(M'')$ are not active in any other node.

@@

Let us discuss rough sizes of the system and expected behaviors.
%
A typical VTS may have about 10 compartments.
%
%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..

The VTS may transport a large number of molecules but the molecules that
are \todo{SA: commented line above} relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%
According to the definition the activity of molecules can be controlled by
the presence of all other molecules.
%
However, in practice the activity of a molecule is controlled by
the presence of ~2-3 other molecules.

>>>>

% \textbf{Fusion condition in BMC and SMT:}
% $\pairs$ defines which molecules can fuse with which molecules.
% %
% Let $\pairs(M')$ denote $\{m|(m,m') \in P \text{ and } m' \in M'\}$.
% %
% $\nodef$ and $\edgef$ are used to define activity of molecules on
% nodes and edges respectively.
% %
% A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
% $\nodef(k,\nlabel(n))$ is true.
% %
% A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
% $\edgef(k,M')$ is true.
% %
% We call $G$ {\em well-structured} if molecules $M$ is divided into
% two equal-sized partitions $M_1$ and $M_2$ such that
% $P \subseteq M_1 \times M_2$, and
% for each $(n,M',n') \in \edges$, $n \neq n'$, 
% $M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
% %
% In other words, a well-structured VTS has no self loops, and 
% each edge carry only those molecules that are present in its source
% and destination nodes.

% We will also consider several variations of the model.
% %
% For example, unique edge between two nodes, activity of molecules is
% not constrained by $\nodef$ and $\edgef$, etc.
% %

% \textbf{Fusion condition in QBF and synthesis:}
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
two partitions $Q$ and $R$ such that
for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
%
In other words,
molecules are of two types $Q$ and $R$,
%
pairing relations have sets of four molecules such that three
are of type $Q$ and one of type $R$ or vice versa.
%
% This distinction of molecules is due to section~\ref{mol-types}.
%
We call $G$ {\em well-structured} if it is pair compatible, and
for each $(n,M',n') \in \edges$, $n \neq n'$ and
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In addition to fuse compatibility, the well-structured property requires that
here are no self loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.
%
An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with its destination node $n'$
and can not fuse with any other node.
%
$\pairs$ models biological possible quadruple of molecules that participate in fusion.
%
Each edge must be uniquely supported by such a quadruple of molecules.
%
We also require three of them to be on the node or edge, and the forth one
to be on the other side of the fusion.
% $\pairs(M'')$ are not active in any other node.

@@

\ashu{Should be written bio people}
Let us discuss rough sizes of the system and expected behaviors.
%
A typical VTS may have about 10 compartments.
%
%Across eukaryotes, there are 20 broad SNARE varieties, though individual species can
%contain higher numbers (humans have 41)~\cite{kloepper2007elaborate}..
%
The VTS may transport a large number of molecules but the molecules that
are \todo{SA: commented line above} relevant of the control of VTS are about 50~\cite{kloepper2007elaborate}.
%
According to the definition the activity of molecules can be controlled by
the presence of all other molecules.
%
However, in practice the activity of a molecule is controlled by
the presence of ~2-3 other molecules.
